---
title: "Oystein Jamming Trials"
author: "LKB"
output: html_document
---

```{r, echo=FALSE}
setwd("d:/a/SimpleUbloxAnalysis")
DataUrl<-file.path(getwd(),"SV.csv")

#knitting settings
require(knitr)
opts_chunk$set(echo = TRUE, cache = TRUE, cache.path = "cache/",  warning=FALSE)
#fig.path = "figure/",
```
# Intro

To run this script make sure that *CheckKeithData.bat* is run first. If I would use dual frequency system I could obtain following information:

ColNo | RinDump | Meaning |
 :---| :---:| :---:
1 | wk | GPS week
2 | secs-of-wk | Seconds of GPS week
3 | sat | SV ID
4 | S5X | L5_SNR
5 | C5X | L5_PR
6 | L5X | L5_CP
7 | S2P | L2_SNR
8 | S1P | L1_SNR
9 | REL | Relativity Correction
10 | SCL | SV Clocks Correction
11 | TRP | Tropo Delay
12 | RNG | Ephemeris Range
13 | AZI | Elev of SV (in relation to user)
14 | ELE | Elev of SV (in relation to user)
15 | C2P | L2_PR P code
16 | C1C | L1_PR C/A code
17 | L2C | L2 CP
18 | L1P | L1_CP

: RinDump output explained

With single frequency uBx chipset only part of this is available to us.


Lets define all types of SV

```{r}
GLONASS=c('R01','R02','R03','R09','R10','R11','R18','R19','R20','R21')
GPS=c('G02','G04','G10','G12','G14','G20','G23','G25','G29','G31')
GPS_IIF='G12'    #transmit','L2C','and','L5)
GPS_IIRM=c('G25','G29','G31')  #transmits','L2C','(and','L5??','how??)
```


# Working with data

##Prepare dataset
```{r, echo=FALSE}
cnames <-c('GPStime','SV_ID','L1_SNR','L1_PR','L1_CP')
cClass <-c('numeric','factor','numeric','numeric','numeric')

GNSS_Data <- read.table(DataUrl, comment.char = "t", header = FALSE, sep = ",", na.strings = "",col.names = cnames)

#Lets see if we set classes properly
sapply(GNSS_Data,class)


#lets add extra column -> GNSSType
GNSS_Data$GNSSType <- ifelse(GNSS_Data$SV_ID %in% GLONASS,'GLO','GPS')

```



##Clean dataset

Do we want to remove anything?
* visible for most of the trials with elevation above 20 deg
* some errous SNR==0 exist. Remove them.

```{r}
#Remove low SV
#LowSV=c('R01','R18','R21','G10','G14','G20','G23')
#GNSS_Data <- subset(GNSS_Data,!(SV_ID %in% LowSV))
#implement this using ELE column


##remove obs with SNR==0
SNRcol <- c('L1_SNR') #all SNR columns
#('L1_SNR','L2_SNR','L5_SNR') #all SNR columns
GNSS_Data[,SNRcol][GNSS_Data[,SNRcol]==0] <- NA

#if u wqant to delete column use
##Data[,c("Date","Time")]<-list(NULL)


```



# Visualising data

###Check for SNR plots
Lets see signal performance using SNR columns only

```{r, echo=FALSE}
library(ggplot2)
#check elevation
plot <- qplot(GPStime,L1_SNR, data = GNSS_Data)
plot + geom_line(aes(colour = GNSSType)) + theme_bw()+facet_wrap(~SV_ID, nrow = 4, ncol = NULL,drop=T)+theme(legend.position="none")+geom_hline(yintercept=20,color="red") + labs(title='SV SNR during trials')



```


